### 2020-02-06 ncov_lancet_ID.tex
research in context

We decompose the basic reproductive number into three key quantities: the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
We use a Bayesian multilevel model to assess uncertainties associated with these quantities.
We apply our framework to compare early estimates of \Ro for the 2019-nCoV outbreak.

@@

We find that most estimates rely on strong assumptions, particularly about the generation-interval dispersion.

@@

@@

We also compare the estimates of \Ro across different studies by 
replacing their values of $r$, $\bar G$, and $\kappa$ with our pooled estimates ($\mu_r$, $\mu_G$, and $\mu_\kappa$, respectively) one at a time and recalculating the basic reproductive number \Ro (\fref{R0}).
This procedure allows us to assess the sensitivity of the estimates of \Ro across appropriate ranges of uncertainties.
We find that incorporating uncertainties one at a time increases the width of the confidence intervals in all but 7 cases.
We estimate narrower confidence intervals for Study 3, Study 6, and Study 7 when we account for proper uncertainties in the generation-interval dispersion because they assume a narrow generation-interval distribution (compare \textbf{base} with \textbf{GI variation} in \fref{R0});
when higher values of $\kappa$ are used, their estimates of \Ro become less sensitive to the values of $r$ and $\bar G$, giving narrower confidence intervals.
We estimate narrower confidence intervals for Study 5 and Study 7 when we account for proper uncertainties in the mean generation interval (compare \textbf{base} with \textbf{GI mean} in \fref{R0}) because the range of uncertainty in the mean generation interval $\bar G$ they consider is much wider than the pooled range (\fref{assumption}).
We also estimate narrower confidence intervals for Study 1 when we substitute their estimated $r$ or $\bar G$ with our pooled estimates for similar reasons.
Substituting the reported $r$ or $\bar G$ from Study 1 with our pooled estimates give narrower confidence intervals for similar reasons.

>>>>

We decompose \Ro into three key quantities: the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
We use a Bayesian multilevel model tomeasure uncertainties associated with these quantities.
We assess early estimates of \Ro for the 2019-nCoV outbreak across these ranges of uncertainties.

@@

We find that most early estimates of \Ro rely on strong assumptions, especially about the generation-interval dispersion.
In particular, estimates that rely on narrow generation-interval distributions are overly sensitive to estimates of the exponential growth rate.

@@

\section*{Research in context}

@@

We also compare the estimates of \Ro across different studies by 
replacing their values of $r$, $\bar G$, and $\kappa$ with our pooled estimates ($\mu_r$, $\mu_G$, and $\mu_\kappa$, respectively) one at a time and recalculating the basic reproductive number \Ro (\fref{R0}).
This procedure allows us to assess the sensitivity of the estimates of \Ro across appropriate ranges of uncertainties.
We find that incorporating uncertainties one at a time increases the width of the confidence intervals in all but 7 cases.
We estimate narrower confidence intervals for Study 3, Study 6, and Study 7 when we account for proper uncertainties in the generation-interval dispersion because they assume a narrow generation-interval distribution (compare \textbf{base} with \textbf{GI variation} in \fref{R0});
when higher values of $\kappa$ are used, their estimates of \Ro become less sensitive to the values of $r$ and $\bar G$, giving narrower confidence intervals.
We estimate narrower confidence intervals for Study 5 and Study 7 when we account for proper uncertainties in the mean generation interval (compare \textbf{base} with \textbf{GI mean} in \fref{R0}) because the range of uncertainty in the mean generation interval $\bar G$ they consider is much wider than the pooled range (\fref{assumption}).
Substituting the reported $r$ or $\bar G$ from Study 1 with our pooled estimates give narrower confidence intervals for similar reasons.
